\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\usetikzlibrary{automata,positioning}

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName\: (\hmwkAuthorEmail)}
\rhead{\hmwkTitle}
% \rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

\setcounter{secnumdepth}{0}
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

\newcommand{\hmwkTitle}{Weekly Update 2/16}
\newcommand{\hmwkClass}{CSE 403 (Wi16)}
\newcommand{\hmwkAuthorName}{Check Your Bias}
\newcommand{\hmwkAuthorEmail}{checkyourbias@u.washington.edu}

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}\\
    \author{\textbf{\hmwkAuthorName\ $\vert$ \hmwkAuthorCSE\ $\vert$ \hmwkAuthorId}}
}

\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

\DeclareMathOperator*{\argmin}{arg\,min}

\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}

\subsection{Previous Week's Plan (2/09)}

Last week's plan was to finish the setup required for the beta release to go smoothly in the implementation phase.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] The plan for this week is to continue working on the models and methods that each model will support for the beta release in 2 weeks.
    \item[Front-end (Aaron, Roee, Geoffrey)] Continue working on the front-end and when the time is right, integrate into the back-end with the methods and modules that are provided (and ask for any additional requirements that may have been missed).
    \item[Full-stack (Sonja, Ryan)] Integrate the crowdsourcing view into the back-end (which needs to be made for the crowdsourced form to be submitted to). Ask for any additional requirements from the back-end team.
\end{description}

\subsection{Progress}

During this week's progress we have made significant progress in finishing most of the features for the beta release, which is due at end of day this Friday.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Finished implementing the database and interface to the frontend that connects all of the data needed to display the application views.
    \item[Front-end (Aaron, Roee, Geoffrey)] Connected the frontend to the backend using the interface that was created by the backend team. Also polished the application views to have a better look to them. Changed the scale that users use to rank candidates to be a 5 point scale instead of a slider.
    \item[Full-stack (Sonja, Ryan)] Completed the crowdsourcing view of the application. Data is first verified on the frontend before it is submitted to the backend when the user hits the submit button.
\end{description}

\subsection{Current Week's Plan}

For this week, our overall goal is to submit our feature complete release before the deadline.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Making our app more open and connected by testing thoroughly / reporting any bugs to the appropriate people.
    \item[Front-end (Aaron, Roee, Geoffrey)] Connecting Firebase to Facebook in order to store the user ids that each user will have when the sign up to use the application.
    \item[Full-stack (Sonja, Ryan)] Validate that data is able to be submitted through the crowdsourcing part of the application. Once submitted, verify that the content can be approved through the application.
\end{description}

\end{document}
