\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\usetikzlibrary{automata,positioning}

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName\: (\hmwkAuthorEmail)}
\rhead{\hmwkTitle}
% \rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

\setcounter{secnumdepth}{0}
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

\newcommand{\hmwkTitle}{Weekly Update 2/23}
\newcommand{\hmwkClass}{CSE 403 (Wi16)}
\newcommand{\hmwkAuthorName}{Check Your Bias}
\newcommand{\hmwkAuthorEmail}{checkyourbias@u.washington.edu}

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}\\
    \author{\textbf{\hmwkAuthorName\ $\vert$ \hmwkAuthorCSE\ $\vert$ \hmwkAuthorId}}
}

\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

\DeclareMathOperator*{\argmin}{arg\,min}

\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}

\subsection{Previous Week's Plan (2/16)}

Last week's plan was to submit our feature complete release before the deadline.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Making our app more open and connected by testing thoroughly / reporting any bugs to the appropriate people.
    \item[Front-end (Aaron, Roee, Geoffrey)] Connecting Firebase to Facebook in order to store the user ids that each user will have when the sign up to use the application.
    \item[Full-stack (Sonja, Ryan)] Validate that data is able to be submitted through the crowdsourcing part of the application. Once submitted, verify that the content can be approved through the application.
\end{description}

\subsection{Progress}

During this week's progress we finished our beta release and implemented the remaining features that were required to have a smooth beta presentation in class on Monday.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Finished implementing the major backend code that was required to perform the profile ranking and the crowdsourcing portions of the application.
    \item[Front-end (Aaron, Roee, Geoffrey)] Fixed many bugs and implemented various fixes for some issues that appeared over the weekend before our beta release presentation. Our app was non-functional before the weekend and this team was able to change that for our presentation.
    \item[Full-stack (Sonja, Ryan)] Completed and submitted content to be used in the app's feed for the presentation. Also worked on bugs that prevented the crowdsourcing from functioning as intended.
\end{description}

In addition to this work, Sonja and Geoffrey presented our app in class with a 10 minute presentation to demo our application to potential customers.

\subsection{Current Week's Plan}

For this week, our overall goal is to finish up any existing bugs and polish our application for the feature complete release, which is due this Friday night.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Work with the crowdsourcing team to finish component.
    \item[Front-end (Aaron, Roee, Geoffrey)] Front-end team is largely done, just finish up the remaining bugs related to frontend code.
    \item[Full-stack (Sonja, Ryan)] Change crowdsourcing to support multiple categories and multiple sources. Also add URL verification to the form as well as fully connect the component to the backend.
\end{description}

\end{document}
