\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\usetikzlibrary{automata,positioning}

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName\: (\hmwkAuthorEmail)}
\rhead{\hmwkTitle}
% \rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

\setcounter{secnumdepth}{0}
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

\newcommand{\hmwkTitle}{Weekly Update 3/01}
\newcommand{\hmwkClass}{CSE 403 (Wi16)}
\newcommand{\hmwkAuthorName}{Check Your Bias}
\newcommand{\hmwkAuthorEmail}{checkyourbias@u.washington.edu}

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}\\
    \author{\textbf{\hmwkAuthorName\ $\vert$ \hmwkAuthorCSE\ $\vert$ \hmwkAuthorId}}
}

\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

\DeclareMathOperator*{\argmin}{arg\,min}

\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}

\subsection{Previous Week's Plan (2/23)}

For last week, our overall goal was to finish up any existing bugs and polish our application for the feature complete release, which was due last Friday night.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Work with the crowdsourcing team to finish component.
    \item[Front-end (Aaron, Roee, Geoffrey)] Front-end team is largely done, just finish up the remaining bugs related to frontend code.
    \item[Full-stack (Sonja, Ryan)] Change crowdsourcing to support multiple categories and multiple sources. Also add URL verification to the form as well as fully connect the component to the backend.
\end{description}

\subsection{Progress}

As a whole, we completed the entire feature complete release in time to meet the deadline last Friday. We also opened a few issues that were found in the final testing phases before the submission.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Fully integrated the crowdsourcing into the backend so that workers may submit content and have that content approved by administrators within the application.
    \item[Front-end (Aaron, Roee, Geoffrey)] Spent the week largely fixing bugs to make the application functional. Bugs included: categories were not defined on candidate pages, hanging tests, ... and more (please see our Github Issues for more).
    \item[Full-stack (Sonja, Ryan)] Added multiple categories and support for multiple sources. Also added URL validation for the sources to that each source is guaranteed to be a URL in the backend.
\end{description}

\subsection{Current Week's Plan}

This week's plan is to finish a release candidate to submit before the Friday deadline.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] This week the backend team will be split along fixing bugs and open issues for the app and also helping the Full-stack team complete the interviews and usability studies.
    \item[Front-end (Aaron, Roee, Geoffrey)] Geoffrey will spend the week completing and assigning bugs / tasks to the team. Aaron and Roee will tackle the task of adding more webdriver tests to ensure that our use cases are well tested.
    \item[Full-stack (Sonja, Ryan)] Crowdsourcing is largely done. A new feature will be added that allows workers to edit / delete their sources and categories after they have been added to the submission form. They will also lead the usability studies and the writeups for the week.
\end{description}

\end{document}
