\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}% http://ctan.org/pkg/listings
\lstset{
  basicstyle=\ttfamily,
  mathescape
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\usetikzlibrary{automata,positioning}

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName\: (\hmwkAuthorEmail)}
\rhead{\hmwkTitle}
% \rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

\setcounter{secnumdepth}{0}
\newenvironment{homeworkProblem}[1][-1]{
    \ifnum#1>0
        \setcounter{homeworkProblemCounter}{#1}
    \fi
    \section{Problem \arabic{homeworkProblemCounter}}
    \setcounter{partCounter}{1}
    \enterProblemHeader{homeworkProblemCounter}
}{
    \exitProblemHeader{homeworkProblemCounter}
}

\newcommand{\hmwkTitle}{Weekly Update 2/9}
\newcommand{\hmwkClass}{CSE 403 (Wi16)}
\newcommand{\hmwkAuthorName}{Check Your Bias}
\newcommand{\hmwkAuthorEmail}{checkyourbias@u.washington.edu}

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}\\
    \author{\textbf{\hmwkAuthorName\ $\vert$ \hmwkAuthorCSE\ $\vert$ \hmwkAuthorId}}
}

\date{}

\renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}

\DeclareMathOperator*{\argmin}{arg\,min}

\DeclareMathOperator*{\argmax}{arg\,max}

\begin{document}

\subsection{Previous Week's Plan (2/02)}

Complete a zero feature release that can be delivered before the deadline.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Implement stubs for the methods and end points to be used with the zero feature release. For now they can return mocked results that can then be used to display the results on the frontend.
    \item[Front-end (Aaron, Roee, Geoffrey)] Complete frontend views that can accomplish the task of a zero feature release by this coming Monday. Including the designs and React components that will be used to implement the ``backend'' experience and functionality of the application.
    \item[Full-stack (Sonja, Ryan)] Complete the product webpage for Check Your Bias and oversee the creation of the crowdsourcing frontend page.
\end{description}

\subsection{Progress}

During this week's progress we finished all of the work required to complete a zero feature release. This included all of the back-end, front-end, full-stack, and website design/work that was necessary.

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] Finished implementing the data models and pre-populating examples into the database that will soon be used to populate the front-end with data.
    \item[Front-end (Aaron, Roee, Geoffrey)] Completed the major views for the application including: Political Profile, Rate Issues, and Candidates. This includes all of the styling also required to make it ``pretty''.
    \item[Full-stack (Sonja, Ryan)] Completed the crowdsourcing front-end that the user will see when the user navigates to submit content within the app. Also completed the \href{https://aaronnech.github.io/CheckYourBias/product_website/}{zero feature release website}, which required a lot of content and back-end work to be completed on Github in order to meet all of the requirements in the specification.
\end{description}

\subsection{Current Week's Plan}

\begin{description}
    \setlength\itemsep{0em}
    \item[Back-end (Nick, Todd, Riley)] The plan for this week is to continue working on the models and methods that each model will support for the beta release in 2 weeks.
    \item[Front-end (Aaron, Roee, Geoffrey)] Continue working on the front-end and when the time is right, integrate into the back-end with the methods and modules that are provided (and ask for any additional requirements that may have been missed).
    \item[Full-stack (Sonja, Ryan)] Integrate the crowdsourcing view into the back-end (which needs to be made for the crowdsourced form to be submitted to). Ask for any additional requirements from the back-end team.
\end{description}

\end{document}
